\documentclass[11pt]{extarticle}
\usepackage[margin=1.5cm]{geometry}
\usepackage[UKenglish]{babel}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\graphicspath{{./pics/}}
\usepackage{hyperref}
\usepackage{changepage}

\begin{document}

\setlength{\parindent}{0pt}

\begin{center}
	\huge
	Protocol for Online Labs

	\vspace{0.5cm}
\end{center}

Every week we'll post the materials for each lab in one of these folders. There will be a video of the lab manager Michael Salvati performing the lab, along with any data and graphs you need. It's your job to write a lab report based on the videos and data provided. We recommend you read the lab manual before watching the video so you know what to expect. \\ 

When writing your report, make sure you include all the relevant components a report should have. Obviously some things are out of your scope, e.g. you won't be able to meddle with the hardware or investigate a source of error, and this is unfortunate, but just do your best to interpret the data we provide. What we give you should be enough to write a complete report. You'll still be able to comment on the experiment setup, perform statistical calculations on the data, and discuss/critique the results. \\ 

Note the lab manuals are the same ones the in-person students are using. They haven't been modified for the online course, so some sections will not be relevant to you [e.g. the sections on programming the lab software and setting up the equipment]. You should still skim over them so you understand what's going on, but you probably don't need to cover them in exhaustive detail. \\ 

For some of the labs we may link you to online simulations where you can adjust parameters and study the output, and you may include your observations from these in your report if you want. \\ 

There are no mandatory lectures or meetings for the online section---you will mostly be working independently and it's up to you to manage your time and keep up with the schedule. Lab reports are due one week after the lab was scheduled. There will be two zoom office hours each week, on Wednesdays from 1-2pm and Fridays from 2-3pm. Anyone may show up to ask questions. \\ 

When you're done with your report, email me a pdf. 

\end{document}
